---
title: "Getting Started with superzarathu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with superzarathu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(superzarathu)
```

# Introduction

`superzarathu` is an R package that simplifies the creation of custom commands for data analysis workflows. It supports both Gemini CLI and Claude Code by automatically generating command files from predefined templates.

## Key Features

This package provides ready-to-use templates for common data analysis tasks:

- **preprocess**: Data cleaning and preparation
- **label**: Data label and factor conversion
- **analysis**: Statistical analysis (descriptive and inferential)
- **shiny**: Interactive web dashboard creation
- **jstable**: Publication-ready statistical tables
- **jskm**: Kaplan-Meier survival curve visualization
- **jsmodule**: Modular Shiny application development

## Quick Start

### For Gemini CLI Users

Generate Gemini CLI command files:

```{r gemini-setup, eval=FALSE}
# Creates .gemini/commands/ directory with TOML files
setup_gemini_commands()
```

After running this function, you can use commands in Gemini CLI:

```bash
gemini preprocess  # Run data preprocess workflow
gemini analysis      # Run statistical analysis workflow
gemini shiny         # Create Shiny application
```

### For Claude Code Users

Generate Claude Code slash commands:

```{r claude-setup, eval=FALSE}
# Creates .claude/commands/ directory with markdown files
setup_claude_commands()
```

After running this function, you can use slash commands in Claude Code:

```
/preprocess  # Run data preprocess workflow
/analysis      # Run statistical analysis workflow  
/shiny         # Create Shiny application
```

## Available Templates

You can explore the available templates and their content:

```{r templates, eval=FALSE}
# Get list of available templates
templates <- get_templates()
names(templates)

# View a specific template
cat(templates$preprocess)
```

### Template Descriptions

- **preprocess**: Complete R workflow for data cleaning, transformation, and preparation using tidyverse
- **label**: Automated and manual data label techniques including codebook integration
- **analysis**: Statistical analysis pipeline with gtsummary for publication-ready tables
- **shiny**: Interactive web dashboard template with filtering and visualization
- **jstable**: Korean medical statistics package for Table 1 and regression tables
- **jskm**: Kaplan-Meier survival analysis with publication-quality plots
- **jsmodule**: Modular Shiny application framework for complex analytics

## Workflow Example

Here's a typical data analysis workflow using the generated commands:

1. **Data preprocess**: Clean and prepare your raw data
2. **Data label**: Apply appropriate labels and factor levels
3. **Statistical Analysis**: Generate descriptive statistics and run models
4. **Interactive Exploration**: Create Shiny dashboard for data exploration
5. **Publication**: Generate publication-ready tables and figures

## Best Practices

- Always start with the `preprocess` template to ensure clean, tidy data
- Use `label` template to make your data human-readable
- Apply `analysis` template for standard statistical workflows
- Consider `shiny` template for interactive data exploration
- Use specialized templates (`jstable`, `jskm`, `jsmodule`) for advanced Korean medical statistics

## Getting Help

Each generated command includes detailed documentation and examples. The templates use placeholder syntax (e.g., `<variable_name>`) that should be replaced with your actual variable names and file paths.

For package documentation:
```{r help, eval=FALSE}
?get_templates
?setup_gemini_commands
?setup_claude_commands
```